Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-19 chi2012.tex

In summary, while data records ranged in complexity, no source subsumed the rest; all contained unique properties other sources did not have.  Moreover, the most common types of heterogeneity exhibited were terminological and value-related, which occurred vastly more than structural or modeling issues.

@@

In order to feel familiar to new users, we borrowed the overall  ``look and feel'' from MacOS Finder-style file managers.  In the DataPalette workspace, shown in Figure \ref{fig:workspace}, the user can freely drag and drop entities from data sources (on the left) into windows that they create, resize, arrange and label. Unlike file managers, however, the basic unit of data was not a file, but an \emph{instance} - corresponding to a single data record, JSON object, RDF instance, or any small bit of structured data. In order to make working with relational graphs manageable, we decided to break up RDF-like relational data into discrete instances with properties. Such chunking was implemented in a generic manner to work with all major Web data feed types (e.g., JSON, XML, RDF).

>>>>

In summary, while data records ranged in complexity, no source subsumed the rest; all contained unique properties.  Moreover, the most common types of heterogeneity exhibited were terminological and value-related, which occurred vastly more than structural or modeling issues.

@@

In order to feel familiar to new users, we borrowed the overall  ``look and feel'' from MacOS Finder-style file managers.  In the DataPalette workspace, shown in Figure \ref{fig:workspace}, the user can freely drag and drop entities from data sources (on the left) into windows that they create, resize, arrange and label. Unlike file managers, the basic unit of data was not a file, but an \emph{instance} - corresponding to a single data record, JSON object, RDF instance, or any small bit of structured data. In order to make working with relational graphs manageable, an early decision we made was to break up RDF-like relational data into discrete instances with properties. This was done at time of import, and could be done for every major Web data feed type (e.g., JSON, XML, RDF) without any loss of generality.
